Incentivizing Exploration by Heterogeneous Users

### 2018-02-06 algorithm.tex

We distinguish two types of agents, based on whether their preference
for their best arm over the second-best arm is ``large'' or ``small''.
To be more precise, we will define (with hindsight) a phase-dependent
cutoff $g(s)$, and for any agent type $\AgV \in \FirstTwo{i}{i'}$,
distinguish whether $\AgV \cdot (\ArmV{i} - \ArmV{i'}) \geq g(s)$ or not.

By Lemma~\ref{lem:sdelta}, the total measure of agents whose
preference is ``small'' in this sense is at most
$\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$ for all $\delta$.
\dkcomment{Put here whatever upper bound we use for these agents.}

@@

For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
\begin{itemize}
\item For those users whose utility difference between their best and
the second best arm is greater than $g(t)$:
we define a sequence of stopping time $\tau_{s}^{k}$ to be the \Kth{k}
time period in the \Kth{s} phase.
For $k > t_{s+1}-t_{s}$, we define $\tau_{s}^{k}=\infty$.
For $\tau_{s}^{k}=t$, the probability of these users making a mistake
is bounded above by
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$,
and the expected regret is bounded above by
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR$.
We denote the regret incurred by these agents by $r_1(\tau_{s}^{k})$.
For $k > t_{s+1}-t_{s}$, we define $r_1(\tau_{s}^{k})=0$.

\item For those user whose utility difference between their best and
the second best arm is smaller than $g(t)$:
this happens with probability \AlmostTied{g(t)} at each time,
and the regret is bounded above by
$\AlmostTied{g(t)} \cdot f(t) \leq \TieDensity f(t)^2$.
We denote the regret incurred by these agents as $r_2(t)$.
\end{itemize}

Thus, the cumulative expected regret incurred up to time $T$ when we
let the agent play myopically is bounded above by:
\begin{align}
\Expect{\sum_{t=1}^{T}r(t)} 
& = \Expect{\sum_{t=1}^{t_{\LatePhase}} r(t) + \sum_{t=t_{\LatePhase}}^{T}(r_1(t)+r_2(t))}  \nonumber \\
& \leq \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
     + \Expect{\sum_{s=\LatePhase}^{T}\sum_{t=t_{s}}^{t_{s+1}-1}r_1(t)}
     + \Expect{\sum_{t=1}^{T}r_2(t)} \nonumber \\
& = \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
     + \Expect{\sum_{s=\LatePhase}^{T} \sum_{k=1}^{\infty}r_1(\tau_{s}^{k})}
     + \Expect{\sum_{t=1}^{T}r_2(t)}. \label{chap5:equ:r1}
\end{align}
Since
\begin{align}
& E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})] \nonumber \\
= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty)+E[r_1(\tau_{n}^{k})|\tau_{n}^{k}=\infty]\times P(\tau_{n}^{k}=\infty)) \nonumber \\
= & \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty), \nonumber
\end{align}

we have
\begin{align}
\eqref{chap5:equ:r1}= & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\left[\sum_{k=1}^{\infty}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right) R\times P(\tau_{n}^{k}<\infty) \right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{chap5:equ:regret}
\end{align}

Thus the cumulative regret at time $T$ is bounded above by
\begin{align}
&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+ & 24\ARMNUM^2 d \frac{1}{e^{\frac{1.8\delta_{0}}{64\Diam^2 d^2\sigma^2}}-1}R+\ARMNUM\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
\end{align}

@@

\begin{align}
\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{equ:regret}
\end{align}

If we set $f^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then
\begin{align}
&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
\leq & \sum_{n=1}^{T} 24\ARMNUM^2 mnR \exp\left(-2\log(T)\right)  + \frac{128\Diam^2 d^2\sigma^2 \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
\leq &  24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1) \nonumber \\
\leq &  12 \ARMNUM^2 d R  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1). \nonumber
\end{align}

>>>>

We distinguish two types of agents, based on whether their preference
for their best arm over the second-best arm is ``large'' or ``small''.
To be more precise, we will define (with hindsight) a time-dependent
cutoff $g(t)$, and for any agent type $\AgV \in \FirstTwo{i}{i'}$,
distinguish whether $\AgV \cdot (\ArmV{i} - \ArmV{i'}) \geq g(t)$ or not.

By Lemma~\ref{lem:sdelta}, the total measure of agents whose
preference is ``small'' in this sense is at most
$\AlmostTied{g(t)} \leq \TieDensity \cdot g(t)$ for all $t$.
\dkcomment{Put here whatever upper bound we use for these agents.}

@@

For the regret incurred when we let the agents play myopically at time $t$ in the $s\geq s_0$ phase, it consists of the following two components:
\begin{itemize}
\item For those users whose utility difference between their best and
the second best arm is greater than $g(t)$:
we define a sequence of stopping time $\tau_{s}^{k}$ to be the \Kth{k}
time period in the \Kth{s} phase.
For $k > t_{s}-t_{s-1}$, we define $\tau_{s}^{k}=\infty$.
For $\tau_{s}^{k}=t$, the probability of these users making a mistake
is bounded above by
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$,
and the expected regret is bounded above by
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR$.
We denote the regret incurred by these agents by $r_1(\tau_{s}^{k})$.
For $k > t_{s}-t_{s-1}$, we define $r_1(\tau_{s}^{k})=0$.

\item For those user whose utility difference between their best and
the second best arm is smaller than $g(t)$:
this happens with probability \AlmostTied{g(t)} at each time,
and the regret is bounded above by
$\AlmostTied{g(t)} \cdot \MAXR \leq \TieDensity\MAXR\cdot f(t)$.
We denote the regret incurred by these agents as $r_2(t)$.
\end{itemize}

Thus, the cumulative expected regret incurred up to time $T$ when we
let the agent play myopically is bounded above by:
\begin{align}
\Expect{\sum_{t=1}^{T}\Regret{t}} 
& = \Expect{\sum_{t=1}^{t_{\LatePhase}} \Regret{t} + \sum_{t=t_{\LatePhase}}^{T}(r_1(t)+r_2(t))}  \nonumber \\
& \leq \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
     + \Expect{\sum_{s=\LatePhase}^{T}\sum_{t=t_{s}}^{t_{s+1}-1}r_1(t)}
     + \Expect{\sum_{t=1}^{T}r_2(t)} \nonumber \\
& = \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
     + \Expect{\sum_{s=\LatePhase}^{T} \sum_{k=1}^{\infty}r_1(\tau_{s}^{k})}
     + \Expect{\sum_{t=1}^{T}r_2(t)}. \label{chap5:equ:r1}
\end{align}
Since
\begin{align}
& E\left[\sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
= &  \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})] \nonumber \\
= &  \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty)+E[r_1(\tau_{s}^{k})|\tau_{s}^{k}=\infty]\times P(\tau_{s}^{k}=\infty)) \nonumber \\
= & \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty), \nonumber
\end{align}

we have
\begin{align}
\eqref{chap5:equ:r1}= & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\left[\sum_{k=1}^{\infty}24\ARMNUM d\exp\left(-\frac{1.8s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right) R\times P(\tau_{s}^{k}<\infty) \right]+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t) \nonumber \\
\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24 \ARMNUM  d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right) \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR\cdot f(t). \label{chap5:equ:regret}
\end{align}

Thus the cumulative regret at time $T$ is bounded above by
\begin{align}
&\sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t)  +\nonumber \\
&O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right). \nonumber 
\end{align}

@@

\begin{align}
\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t). \label{equ:regret}
\end{align}

If we set $f^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then
\begin{align}
&\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t) \nonumber \\ 
\leq & \sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  + \frac{128\Diam^2 d^2\sigma^2 \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{t} \nonumber \\
\leq &  24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1) \nonumber \\
\leq &  12 \ARMNUM^2 d R  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1). \nonumber
\end{align}

### 2018-02-06 problem_setting.tex

\dkcomment{Do we need this definition here?}
We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the
\emph{starting point of the $n^{th}$ round}.
We call the set of times $[t_{n}, t_{n+1})$ the
\emph{$n^{th}$ round}.

@@

Let $\FirstTwo{i}{i'} = \Set{\AgV}{\Best{\AgV} = i, \Second{\AgV} = i'}$
be the set of agent attribute vectors whose best arm is $i$ and
second-best arm is $i'$.
Let $F_{i,i'}$ be the marginal cumulative density function
(or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
of $(\ArmV{i}-\ArmV{i'}) \cdot \AgV$,
conditioned on $\AgV \in \Omega_{i,j}$.
In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the
preference of a random agent for arm $i$ over arm $i'$, given that
$i$ and $i'$ are the agent's first and second choices.

>>>>

\dkcomment{Do we need this definition here?}
We call time $t_{n}=\min_{t}\{\forall i, \NumPull{t}{i} \geq n\}$ the
\emph{starting point of the $n^{th}$ round}.
We call the set of times $[t_{n}, t_{n+1})$ the
\emph{$n^{th}$ round}.

@@

Let $\FirstTwo{i}{i'} = \Set{\AgV}{\Best{\AgV} = i, \Second{\AgV} = i'}$
be the set of agent attribute vectors whose best arm is $i$ and
second-best arm is $i'$.
Let $F_{i,i'}$ be the marginal cumulative density function
(or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
of $(\ArmV{i}-\ArmV{i'}) \cdot \AgV$,
conditioned on $\AgV \in \Omega_{i,i^{'}}$.
In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the
preference of a random agent for arm $i$ over arm $i'$, given that
$i$ and $i'$ are the agent's first and second choices.
